---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# dmsepmlr

<!-- badges: start -->
<!-- badges: end -->

**D**elta **M**ethod **S**tandard **E**rrors for various quantities related to the **P**redictive **M**argins of a **L**ogistic **R**egression model with a binary main effect and any number of adjustors.

 This package estimates predictive margins, along with their delta method standard errors, for a logistic regression model having a binary main effect and any number of adjustors.  The margins are then used to produce additional estimates, including an "adjusted risk difference" and an "adjusted risk ratio."

## Installation

You can install the development version of dmsepmlr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jameshenegan/dmsepmlr")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(dmsepmlr)
library(haven)
dat <- read_dta("http://www.stata-press.com/data/r13/margex.dta")
logMarginsResults <- logisticMargins(formula = outcome ~ treatment + distance,
                                     main_effect = "treatment",
                                     over = FALSE,
                                     data = dat)
logMarginsResults
```
